---
name: Logan Stundal
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: PhD
position: PhD Candidate
address: Minneapolis, MN
phone: 701 610 8586
email: stund005@umn.edu
www: loganstundal.com
github: loganstundal
linkedin: logan-stundal
twitter: loganstundal
headcolor: 414141
output: vitae::awesomecv
keep_tex: true
header-includes:
   - \usepackage{xcolor}
   - \definecolor{fontColor}{HTML}{414141}
# knit: (function(inputFile, encoding) { 
#     rmarkdown::render(inputFile, 
#                       encoding    = encoding, 
#                       output_file = file.path(dirname(inputFile),
#                                               'Versions',
#                                               paste0('VITAE_',format(lubridate::today(), "%Y%m%d")))) 
#                       })
---

<!---------------------------------------------------------------------------->
```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```
<!---------------------------------------------------------------------------->



<!---------------------------------------------------------------------------->
# Education
<!---------------------------------------------------------------------------->
```{r}
umn <- tribble(
  ~ degree, ~ uni, ~ loc, ~ dates,
  "PhD, Political Science", "University of Minnesota", "Minneapolis, MN", "2016 - Present",)

umn.details <- c("Fields: International Relations and Political Methods",
                 "Advisor: Tanisha Fazal; Committee: John Freeman, Mark Bell, Jessica Stanton")

und <- tribble(
  ~ degree, ~ uni, ~ loc, ~ dates,
  "BA, Political Science and Economics", "University of North Dakota", "Grand Forks, ND", "2013"
)
und.details <- c("Magna Cum Laude")



detailed_entries(data = umn, what = degree, when = dates, 
                 with = uni, where = loc, why = umn.details)
detailed_entries(data = und, what = degree, when = dates, 
                 with = uni, where = loc, why = und.details,.protect=F)

```
<!---------------------------------------------------------------------------->



<!---------------------------------------------------------------------------->
# Dissertation
```{r}
tribble(~title, ~abstract,
        "The Epidemiology of Civil Wars", 
        "My dissertation explores the causal relationship between the dynamics of civil war and the outbreak of disease within these environments. It examines how certain classes of conflict produce differential civilian strategic responses which yield different disease outbreak outcomes. Cross-national and sub-national dynamic spatial models demonstrate theoretical generalizability while detailed case analysis of the Syrian civil war illuminates causal mechanisms.") %>%
  detailed_entries(what = title,
                   why  = abstract)
```
<!---------------------------------------------------------------------------->



<!---------------------------------------------------------------------------->
# Publications
<!---------------------------------------------------------------------------->
\vspace{3mm}
Under review
\vspace{-3mm}
```{r}
tribble(~title, ~coauthors, ~year,
        "Human Rights Violations in Space: Assessing the External Validity of Machine Geo-coded Vs. Human Geo-coded Data. Accepted by \\it{Political Analysis}", "(with Benjamin Bagozzi, John Freeman, and Jennifer Holmes)", "2021") %>%
  detailed_entries(what = title,
                   when = year,
                   why  = coauthors,
                   .protect = FALSE)
```

\vspace{3mm}
Working papers and Presentations
\vspace{-3mm}
```{r}
tribble(~title, ~coauthors, ~conference,
        "Computationally Efficient Spatial and Spatiotemporal models estimated with Non-linear Least Squares", NA, NA,
        "Pluralism in Time Series Analysis", NA, "APSA 2021",
        "Mapping US and Chinese Health Diplomacy", "(with Tanisha Fazal)", "ISA 2021; APSA 2021",
        "Disease and War: Why conflict context matters and how it shapes disease outcomes", NA, "ISA 2021",
        "Rebel Predation and Foreign Aid", NA, "MPSA 2019") %>%
  detailed_entries(what = title,
                   why  = coauthors,
                   when = conference)
```

\vspace{3mm}
Non-academic writing
\vspace{-3mm}
```{r}
tribble(~title, ~when,
        "``Measles, Ukraine, and Civil War: The Missing Links'' (with Tanisha Fazal). \\it{Political Violence @ A Glance}", "March 2019") %>%
  detailed_entries(what = title, 
                   when = when,
                   .protect = F)
```
<!---------------------------------------------------------------------------->



<!---------------------------------------------------------------------------->
# Awards, Grants, & Fellowships
<!---------------------------------------------------------------------------->
```{r}
tribble(
  ~name, ~year,
  "Political Science, Teaching Assistant Fellowship", "2017-Present",
  "Political Science, Summer Fellowship", "2017-Present",
  "National Science Foundation, GRFP Honorable Mention", "2018",
  "Graduate Pre-Dissertation Research Fellowship", "2017",
  "Larson Graduate Research Fellowship in Political Economy", "2016-17",
  "EITM Certification / Fellowship - ICPSR (NSF Funded)", "2017",
  "PolMeth Travel Grant, Madison, WI (NSF Funded)", "2017",
  "Ronald E. McNair Post-Baccalaureate Fellowship", "2009-13"
  ) %>%
  brief_entries(what = name,
                with = year)

```
<!---------------------------------------------------------------------------->


\pagebreak

<!---------------------------------------------------------------------------->
# Teaching and Research Experience
<!---------------------------------------------------------------------------->
```{r}
tribble(~what, ~description, ~when,
        'Teaching Assistant',
        c('POL 1025: Global Politics; POL 1026: Foreign Policy; POL 3085: Quantitative Analysis; POL 4810: The Politics of Nuclear Weapons; POL 4991: Capstone'), NA,
        
        'ICPSR Graduate Student Instructor', "(Empirical Modeling with Robert Franzese)", "2020, 2021",
        
        "ICPSR Workshop, Guest Lecturer","(Spatial Econometrics with Robert Franzese)", "2020, 2021",
        
        "Course Instructor", "POL 3085: Quantitative Analisys", "Summer 2019") %>%
  detailed_entries(what = what,
                   why  = description,
                   when = when)
```

Research Assistantships
```{r}
tribble(
  ~what, ~year,
  "Tanisha Fazal", "2021 - present",
  "John Freeman", "2018 - present",
  "Ron Krebs", "Fall 2019",
  "Jessica Stanton", "Summer 2018"
  ) %>%
  brief_entries(what = what,
                with = year)

```
<!---------------------------------------------------------------------------->



<!---------------------------------------------------------------------------->
# Conference & Workshop Participation
<!---------------------------------------------------------------------------->
Annual Meetings 
```{r}
tribble(~name, ~year,
        "APSA", "2021",
        "Polmeth", "2017, 2019, 2021",
        "ISA", "2021",
        "Midwest Political Science Association", "2019, 2020",
        "Upper Midwest International Relations Conference", "2018, 2019") %>%
  brief_entries(what = name,
                with = year)
```

Workshops
```{r}
tribble(~name, ~year,
        "Mapping US and Chinese Health Diplomacy", "2021",
        "BIGCSS Summer School in Computational Social Science (Breman, Germany)", "Summer 2018",
        "ICPSR, University of Michigan, Ann Arbor", "Summer 2017") %>%
  brief_entries(what = name,
                with = year)
```
<!---------------------------------------------------------------------------->



<!---------------------------------------------------------------------------->
# Service
<!---------------------------------------------------------------------------->
```{r}

tribble(
  ~name, ~year,
  "Minnesota Political Methods Colloquium, Co-Chair", "2018-Present",
  "Minnesota Graduate Student Methods Conference, Organizer", "2018-2020",
  "McNair Program: Student Mentor","2017-Present",
  "Graduate Student Life Committee, Co-Chair", "2018-19",
  "TRIO Program - Upward Bound: Mentor", "2016"
  ) %>%
  brief_entries(what = name,
                with = year)
```
<!---------------------------------------------------------------------------->



<!---------------------------------------------------------------------------->
# Affiliations
<!---------------------------------------------------------------------------->
```{r}
tribble(~what,
        "American Political Science Association",
        "Society for Political Methodology",
        "Midwest Political Science Association",
        "International Studies Association") %>%
  brief_entries(what = what)
```
<!---------------------------------------------------------------------------->

\pagebreak

<!---------------------------------------------------------------------------->
# Skills
<!---------------------------------------------------------------------------->
Research Interests
```{r}
tribble(~detail,
        "\\textbf{International Relations}: Disease outbreaks, civil wars, political violence/conflict processes, humanitarian crises",
        "\\textbf{Methodology}: spatial models, diffusion and contagion processes, Bayesian analsysis, simulation"
        ) %>%
  brief_entries(detail,.protect = F)
```

Data Analysis
```{r}
tribble(~detail,
        "Spatial Econometrics, Mapping, Time Series, Bayesian Analysis, Visualisation, Data Cleaning, Surveys",
        ) %>%
  brief_entries(detail)
```

Programming
```{r}
tribble(~detail,
        "R, Python, SQL, Stan, LaTeX, Git, Javascript"
        ) %>%
  brief_entries(detail)
```
<!---------------------------------------------------------------------------->



<!---------------------------------------------------------------------------->
# Awards & Achievements
<!---------------------------------------------------------------------------->
Awards
```{r}
tribble(
  ~ award, ~ year,
  "UMN, Thank a Teacher Award", "2018, 2019",
) %>%
  brief_entries(what = award, 
                with = year)
```
<!---------------------------------------------------------------------------->



\pagebreak



<!---------------------------------------------------------------------------->
# References
<!---------------------------------------------------------------------------->
```{r}

tribble(~what, ~rank, ~why,
        "Tanisha Fazal", "Professor", list("Political Science Department", "University of Minnesota", "Email: \\href{mailto:fazal007@umn.edu}{fazal007@umn.edu}", "Phone: 612-624-8261"),
        
       "John Freeman", "Professor", list("Political Science Department", "University of Minnesota", "Email: \\href{mailto:freeman@umn.edu}{freeman@umn.edu}", "Phone: 612-624-6018"),
       
       "Jessica Stanton", "Associate Professor", list("Political Science Department", "Temple University", "Email: \\href{mailto:jessica.stanton@temple.edu}{jessica.stanton@temple.edu}"),
       
       "Mark Bell", "Associate Professor", list("Political Science Department", "University of Minnesota", "Email: \\href{mailto:msbell@umn.edu}{msbell@umn.edu}", "Phone: 612-624-4144"),
       
       "Robert Franzese", "Professor", list("Political Science Department", "University of Michigan", "Email: \\href{mailto:franzese@umich.edu}{franzese@umich.edu}")
       ) %>% 
  detailed_entries(what = what,
                   when = rank,
                   why  = why,
                   .protect = FALSE)

```


  <!-- \vspace{3in} -->
  
  
  <!-- \begin{table}[!h] -->
  <!--   \fontsize{10}{4} -->
  <!--   \selectfont -->
  <!--   {\color{fontColor}\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} lll} -->
  <!--     John Freeman                                & Tanisha Fazal                     & Jessica Stanton \\ -->
  <!--     Professor                                   & Associate Professor               & Associate Professor\\ -->
  <!--     Political Science Department                & Political Science Department      & Humphrey School of Public Affairs\\  -->
  <!--     University of Minnesota                     & University of Minnesota           & University of Minnesota \\ -->
  <!--     Email: \href{mailto:freeman@umn.edu}{freeman@umn.edu} & -->
  <!--     Email: \href{mailto:fazal007@umn.edu}{fazal007@umn.edu} & -->
  <!--     Email: \href{mailto:stantonj@umn.edu}{stantonj@umn.edu} \\ -->
  <!--     Phone: 612-624-6018                         & Phone: 612-624-8261 \             & 612-626-8910 \\ -->
  <!--     & & \\ -->
  <!--     & & \\ -->
  <!--     & & \\ -->
  <!--     Jane Sumner                                 & Mark Bell                         & Brian Urlacher \\ -->
  <!--     Assistant Professor                         & Assistant Professor               & Professor \\  -->
  <!--     Political Science Department                & Political Science Department      & Political Science Department\\  -->
  <!--     University of Minnesota                     & University of Minnesota           & University of North Dakota \\ -->
  <!--     Email: \href{mailto:jlsumner@umn.edu}{jlsumner@umn.edu} & -->
  <!--     Email: \href{mailto:msbell@umn.edu}{msbell@umn.edu} & -->
  <!--     Email: \href{mailto:brian.urlacher@und.edu}{brian.urlacher@und.edu} \\ -->
  <!--     Phone: 612-626-7825                         & Phone: 612-626-2889               & Phone: 701-777-3541 -->
  
  
  <!--   \end{tabular*}} -->
  <!-- \end{table} -->
<!---------------------------------------------------------------------------->

