---
name: Logan Stundal
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: PhD
position: PhD Candidate
address: Minneapolis, MN
phone: 701 610 8586
email: stund005@umn.edu
www: loganstundal.com
github: loganstundal
# linkedin: loganstundal
twitter: loganstundal
headcolor: 414141
output: vitae::awesomecv
keep_tex: true
header-includes:
   - \usepackage{xcolor}
   - \definecolor{fontColor}{HTML}{414141}
# knit: (function(inputFile, encoding) { 
#     rmarkdown::render(inputFile, 
#                       encoding    = encoding, 
#                       output_file = file.path(dirname(inputFile),
#                                               'Versions',
#                                               paste0('VITAE_',format(lubridate::today(), "%Y%m%d")))) 
#                       })
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```


# Education
```{r}
umn <- tribble(
  ~ degree, ~ uni, ~ loc, ~ dates,
  "PhD, Political Science", "University of Minnesota", "Minneapolis, MN", "2016 - Present",)

umn.details <- c("Fields: International Relations and Political Methods",
                 "Advisors: John Freeman, Tanisha Fazal")

und <- tribble(
  ~ degree, ~ uni, ~ loc, ~ dates,
  "BA, Political Science and Economics", "University of North Dakota", "Grand Forks, ND", "2013"
)
und.details <- c("Magna Cum Laude")



detailed_entries(data = umn, what = degree, when = dates, 
                 with = uni, where = loc, why = umn.details)
detailed_entries(data = und, what = degree, when = dates, 
                 with = uni, where = loc, why = und.details,.protect=F)

```


# Dissertation
Placeholder


# Working Papers
```{r}
tribble(~title, ~coauthors,
        "Event Data in Space: Statistical Models of Machine Coded Vs. Human Coded Data", 
        "(with Benjamin Bagozzi, John Freeman, and Jennifer Holmes), Presented at PolMeth 2019",
        "Rebel Predation and Foreign Aid", "Presented at MPSA 2019") %>%
  detailed_entries(why = coauthors,what = title)
```


# Non-academic writing
```{r}
tribble(~entry,~when,
        "``Measles, Ukraine, and Civil War: The Missing Links'' (with Tanisha Fazal). \\it{Political Violence @ A Glance}", "March 22, 2019") %>%
  detailed_entries(what = entry, 
                   when = when,.protect=F)
```


# Awards, Grants, & Fellowships
```{r}
tribble(
  ~name, ~year,
  "Political Science, Teaching Assistant Fellowship", "2017-Present",
  "Political Science, Summer Fellowship", "2017-Present",
  "National Science Foundation, GRFP Honorable Mention", "2018",
  "Graduate Pre-Dissertation Research Fellowship", "2017",
  "Larson Graduate Research Fellowship in Political Economy", "2016-17",
  "EITM Certification / Fellowship - ICPSR (NSF Funded)", "2017",
  "PolMeth Travel Grant, Madison, WI (NSF Funded)", "2017",
  "Ronald E. McNair Post-Baccalaureate Fellowship", "2009-13"
  
  ) %>%
  brief_entries(what = name,
                with = year)

```


# Teaching and Research Experience
```{r}
tribble(~what, ~why,
        'Teaching Assistant',
        c('POL 1025: Global Politics; POL 1026: Foreign Policy; POL 3085: Quantitative Analysis; POL 4810: The Politics of Nuclear Weapons')) %>%
  detailed_entries(what = what,
                   why  = why)

tribble(~what,'Course Instructor') %>%
  detailed_entries(what = what,
                   why  = c('POL 3085: Quantitative Analysis; Summer 2019'))

tribble(~what,'Research Assistant') %>%
  detailed_entries(what = what,
                   why  = c('John Freeman: Summer 2018 - present',
                            'Ron Krebs: Fall 2019',
                            'Jessica Stanton: Summer 2018'))

```

\pagebreak


# Conference & Workshop Participation
Annual Meetings 
```{r}
tribble(~name, ~year,
        "Polmeth", "2019, 2017",
        "Midwest Political Science Association", "2020,2019",
        "Upper Midwest International Relations Conference", "2019, 2018") %>%
  brief_entries(what = name,
                with = year)
```

Workshops
```{r}
tribble(~name, ~year,
        "BIGCSS Summer School in Computational Social Science (Breman, Germany)", "Summer 2018",
        "ICPSR, University of Michigan, Ann Arbor", "Summer 2017") %>%
  brief_entries(what = name,
                with = year)
```


# Service
```{r}

tribble(
  ~name, ~year,
  "Minnesota Graduate Student Methods Conference, Organizer", "2018-Present",
  "Minnesota Political Methods Colloquium, Co-Chair", "2018-Present",
  "McNair Program: Student Mentor","2017-Present",
  "Graduate Student Life Committee, Co-Chair", "2018-19",
  "TRIO Program - Upward Bound: Mentor", "2016"
  ) %>%
  brief_entries(what = name,
                with = year)
```


# Affiliations
```{r}
tribble(~what,
        "Society for Political Methodology",
        "Midwest Political Science Association",
        "International Studies Association") %>%
  brief_entries(what = what)
```


# Relevant Skills
Research Interests
```{r}
tribble(~detail,
        "\\textbf{International Relations}: Disease outbreaks, civil wars, political violence/conflict processes, humanitarian crises",
        "\\textbf{Methodology}: spatial models, diffusion and contagion processes, Bayesian analsysis, simulation"
        ) %>%
  brief_entries(detail,.protect = F)
```

Data Analysis
```{r}
tribble(~detail,
        "Spatial Econometrics, Mapping, Time Series, Bayesian Analysis, Visualisation, Data Cleaning, Surveys",
        ) %>%
  brief_entries(detail)
```

Programming
```{r}
tribble(~detail,
        "R, Python, SQL, Stan, LaTeX, Git"
        ) %>%
  brief_entries(detail)
```

# Awards & Achievements
Awards
```{r}
tribble(
  ~ award, ~ year,
  "UMN, Thank a Teacher Award", "2019, 2018",
) %>%
  brief_entries(what = award, 
                with = year)
```

# References
\begin{table}[!h]
  \fontsize{10}{4}
  \selectfont
  {\color{fontColor}\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} lll}
    John Freeman                                & Tanisha Fazal                     & Jessica Stanton \\
    Professor                                   & Associate Professor               & Associate Professor\\
    Political Science Department                & Political Science Department      & Humphrey School of Public Affairs\\ 
    University of Minnesota                     & University of Minnesota           & University of Minnesota \\
    Email: \href{mailto:freeman@umn.edu}{freeman@umn.edu} &
    Email: \href{mailto:fazal007@umn.edu}{fazal007@umn.edu} &
    Email: \href{mailto:stantonj@umn.edu}{stantonj@umn.edu} \\
    Phone: 612-624-6018                         & Phone: 612-624-8261 \             & 612-626-8910 \\
    & & \\
    & & \\
    & & \\
    Jane Sumner                                 & Mark Bell                         & Brian Urlacher \\
    Assistant Professor                         & Assistant Professor               & Professor \\ 
    Political Science Department                & Political Science Department      & Political Science Department\\ 
    University of Minnesota                     & University of Minnesota           & University of North Dakota \\
    Email: \href{mailto:jlsumner@umn.edu}{jlsumner@umn.edu} &
    Email: \href{mailto:msbell@umn.edu}{msbell@umn.edu} &
    Email: \href{mailto:brian.urlacher@und.edu}{brian.urlacher@und.edu} \\
    Phone: 612-626-7825                         & Phone: 612-626-2889               & Phone: 701-777-3541
    
    
  \end{tabular*}}
\end{table}


